The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-03-23 SC-challenge.tex
added notes for each of us
cleaned up acknowledgements a bit

\definecolor{blueish}{rgb}{0.2,0.2,0.8}
\newcommand{\note}[1]{ {\textcolor{blueish}    { ***Note:      #1 }}}

@@

\begin{bottomstuff}
Some work by K.\ E.\ Niemeyer was supported by NSF grant ACI-1535065.
Work by D.\ S.\ Katz was supported by the National Science Foundation (NSF) while working at the Foundation; any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.

>>>>

\definecolor{blueish}{rgb}{0.2,0.2,0.8}
\newcommand{\katznote}[1]{ {\textcolor{blueish} { ***DSK: #1 }}} % Dan
\newcommand{\knnote}[1]{ {\textcolor{orange} { ***KEN: #1 }}} % Kyle
\newcommand{\asnote}[1]{ {\textcolor{red} { ***AMS: #1 }}} %Arfon

@@

\begin{bottomstuff}
Work by K.\ E.\ Niemeyer was supported in part by the National Science Foundation (NSF) under grant ACI-1535065.
Work by D.\ S.\ Katz was supported by the NSF while working at the Foundation; any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.
